---
title: "Capital City Populations Australia"
author: "Leesa Cromie"
date: "3/13/2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Capital City Populations Australia

This presentation is going to look at the growth of Australian Capital cities from 2019 - 2020.

- The data is downloadable from [Australian Bureau of Statistics](https://www.abs.gov.au/statistics/people/population/regional-population/latest-release#data-download)

- Plotly has been used to create a barchart for the estimated population in 2019 and 2020 for each Australian capital city.

- It can be seen from the next slide that all capital cities except Darwin had a small increase from 2019 to 2020.

Reference: Australian Bureau of Statistics: Regional Populations, <http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har> (Accessed 10 Mar 2022)

```{r dataread, echo = FALSE}

cities<-data.frame(read.csv("Australian Bureau of Statistics.csv", header = TRUE, na.strings = c("", "NA")))
cities<- na.omit(cities)
cities<-cities[1:8,]
colnames(cities) <-c("City", "Year_2020", "Increase", "Percentage" )
cities$Year_2020<-gsub(",","",cities$Year_2020)
cities$Increase <- gsub(",","",cities$Increase)
cities$Year_2020 <-as.numeric(cities$Year_2020)
cities$Increase <-as.numeric(cities$Increase)
Year_2019<-cities$Year_2020 - cities$Increase
cities <- cbind(cities, Year_2019)
```
## Australian Capital City Estimated Populations 2019 and 2020.

```{r plot, echo = FALSE, warning=FALSE, message=FALSE}
library(plotly)

fig<-plot_ly(cities, x = ~City, y = ~Year_2019, type = "bar", name = "2019")
fig<-fig %>% add_trace(y=~Year_2020, name = "2020")
fig<-fig%>% layout(yaxis = list(title = "ERP"), barmode = "group")

fig

```
